\chapter*{\centering \begin{normalsize}Acknowledgements\end{normalsize}}

\thispagestyle{plain}
\addcontentsline{toc}{chapter}{\numberline{}Acknowledgements}

\begin{quotation}
\noindent First of all, I would like to give a huge thanks to my supervisor Nikhil Bansal. I learned so much during (the research for) this thesis about subjects that interest me, more than this thesis could ever contain. You have only encouraged me to absorb all that knowledge and broaden my horizons. You showed me fascinating results on all related topics and problems and inspired me by researching all that might be interesting for my academic future. Thank you for everything you have done to make me a better researcher.

I would like to thank my future (co-)promotor Tjark Vredeveld; your interest in the thesis and me has contributed to my confidence as a researcher and my general feeling of well-being. Thank you, I'm looking forward to our cooperation in the years to come.

I also owe a thank you to my fellow student Annette Ficker, with whom I initially researched various interesting problems until we parted ways when I chose $k$-set packing as my subject and you chose 2-dimensional bin packing for your thesis. Thank you for the fruitful discussions about everything we encountered and of course for the very nice time we had together during university.

I also would like to thank some other people who discussed the problem with me, among which are authors of some papers I read. In particular I would like to thank Per Austrin, Fabrizio Grandoni, Konstantin Makarychev, Monaldo Mastrolilli, Viswanath Nagarajan and Ruben van der Zwaan for their time.

A big thank you to the teachers in the combinatorial optimization group for their interesting and inspiring classes: Nikhil Bansal, Cor Hurkens, Judith Keijsper, Rudi Pendavingh and Gerhard Woeginger. A special thanks to Jan Draisma and Gerhard Woeginger for forming the assessment committee for my thesis.

Also I want to thank some other fellow students, in particular Jorn van der Pol and Reint den Toonder, for their interest in the thesis, their general support and of course their friendly company for the past years.

Finally a thanks to my family and boyfriend for their support and faith. I would not be where I am today if it weren't for you. A huge thanks to all of you.
\end{quotation} 