\documentclass{amsart}

%%% packages %%%

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[all]{xy}
\usepackage{graphicx}
%\usepackage{showkeys}


\sloppy



%%% theorems %%%
\theoremstyle{plain}

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{fact}[thm]{Fact}
\newtheorem{cor}[thm]{Corollary}
\newtheorem*{claim}{Claim}
\newtheorem*{conj}{Conjecture}

\theoremstyle{definition}

\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ex}[thm]{Example}
\newtheorem*{note}{Notation}





%%% blackboard fonts %%%

\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}





%%% other fonts %%%

\newcommand{\A}{\mathcal{A}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\calO}{\mathcal{O}}





%%% commands %%%

\newcommand{\abs}[1]{\lvert {#1} \rvert}

\newcommand{\calH}{\mathcal{H}}
\newcommand{\Conf}{\mathrm{Conf}\,}

\newcommand{\emb}[2]{\mathcal{K}_{#1 ,#2}}

\newcommand{\femb}[2]{\tilde{\mathcal{K}}_{#1 ,#2}}

\newcommand{\gr}{\mathrm{gr}}

\newcommand{\I}{\mathcal{I}}
\newcommand{\id}{\mathrm{id}}
\newcommand{\img}{\mathrm{im}\,}
\newcommand{\Int}{\mathrm{Int}\,}

\newcommand{\ord}{\mathrm{ord}\,}

\newcommand{\pair}[2]{\langle {#1},\, {#2}\rangle}

\newcommand{\rank}{\mathrm{rank}\,}

\newcommand{\sym}{\mathfrak{S}_k}





\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}




\title[Configuration space integrals and the Haefliger invariant]
{Configuration space integrals for embedding spaces and the Haefliger invariant}
\author{Keiichi Sakai}
\date{\today}
\address{Graduate School of Mathematical Sciences, University of Tokyo}
\email{ksakai@ms.u-tokyo.ac.jp}
\urladdr{http://www.ms.u-tokyo.ac.jp/~ksakai/index.html}

\subjclass[2000]{Primary~58D10; Secondary~57Q45, 81Q30}
\keywords{The space of long $j$-knots; Graph complex; Configuration space integral; Haefliger invariant}

\begin{document}


\begin{abstract}
Let $\emb{n}{j}$ be the space of long $j$-knots in $\R^n$.
In this paper we introduce a graph complex $\D^*$ and a linear map $I:\D^* \to \Omega^*_{DR}(\emb{n}{j})$ via
configuration space integral, and prove that
(1) when both $n>j\ge 3$ are odd, $I$ is a cochain map if restricted to graphs with at most one loop component,
(2) when $n-j \ge 2$ is even, $I$ is a cochain map if restricted to tree graphs, and
(3) when $n-j \ge 3$ is odd, $I$ added a correction term produces a $(2n-3j-3)$-cocycle of $\emb{n}{j}$ which gives a new
formulation of the Haefliger invariant when $n=6k$, $j=4k-1$ for some $k$.
\end{abstract}

\maketitle

\input{Haefliger_intro}

\input{Haefliger_graph}

\input{Haefliger_conf}

\input{Haefliger_inv_original}

\input{Haefliger_vanish}

%\bibliography{biblio}
\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
% \MRhref is called by the amsart/book/proc definition of \MR.
\providecommand{\MRhref}[2]{%
  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
}
\providecommand{\href}[2]{#2}
\begin{thebibliography}{10}

\bibitem{AltschulerFreidel97}
D.~Altschuler and L.~Freidel, \emph{Vassiliev knot invariants and Chern-Simons perturbation theory to all orders},
 Comm.\ Math.\ Phys.\ \textbf{187} (1997), no.~2, 261--287.

\bibitem{AxelrodSinger94}
S.~Axelrod and I.~M. Singer, \emph{Chern-Simons perturbation theory II},
 J.\ Diff.\ Geom.\ \textbf{39} (1994), 173--213.

\bibitem{BottTaubes94}
R.~Bott and C.~Taubes, \emph{On the self-linking of knots},
 J.\ Math.\ Phys.\ \textbf{35} (1994), no.~10, 5247--5287.

\bibitem{Budney08}
R.~Budney, \emph{A family of embedding spaces},
 Geom.\ Topol.\ Monogr.\ \textbf{13} (2008), 41--84.

\bibitem{CCL02}
A.~Cattaneo, P.~Cotta-Ramusino, and R.~Longoni, \emph{Configuration spaces and Vassiliev classes in any dimensions},
 Algebr.\ Geom.\ Topol.\ \textbf{2} (2002), 949--1000.

\bibitem{CattaneoRossi05}
A.~Cattaneo and C.~Rossi, \emph{Wilson surfaces and higher dimensional knot invariants},
 Comm.\ Math.\ Phys.\ \textbf{256} (2005), no.~3, 513--537.

\bibitem{HabiroKanenobuShima99}
K.~Habiro, T.~Kanenobu and A.~Shima, \emph{Finite type invariants of ribbon $2$-knots},
 Contemp.\ Math.\ vol.\ 233, 187--196.

\bibitem{Haefliger62}
A.~Haefliger, \emph{Knotted $(4k-1)$-spheres in $6k$-space},
 Ann.\ of Math.\ (2) \textbf{75} (1962), 452--466.

\bibitem{Haefliger66}
\bysame, \emph{Differential embeddings of $S\sp{n}$ in $S\sp{n+q}$ for $q>2$},
 Ann.\ of Math.\ (2) \textbf{83} (1966), 402--436.

\bibitem{Kohno94}
T.~Kohno, \emph{Vassiliev invariants and de Rham complex on the space of knots},
 Contemp.\ Math.\ vol.\ 179, 123--138.

\bibitem{Longoni04}
R.~Longoni, \emph{Nontrivial classes in $H^*(\text{Imb}\, (S^1 ,\R^n ))$ from nontrivalent graph cocycles},
 Int.\ J.\ Geom.\ Methods Mod.\ Phys.\ \textbf{1} (2004), no.~5, 639--650.

\bibitem{Roseman89}
D.~Roseman, \emph{Spinning knots about submanifolds; spinning knots about projections of knots},
 Topology Appl.\ \textbf{31} (1989), no.~3, 225--241.

\bibitem{RosemanTakase07}
D.~Roseman and M.~Takase, \emph{High-codimensional knots spun about manifolds},
  Algebr.\ Geom.\ Topol.\ \textbf{7} (2007), 359--377.

\bibitem{Rossi_thesis}
C.~Rossi, \emph{Invariants of higher-dimensional knots and topological quantum field theories},
 Ph.D.\ thesis, Zurich University, 2002.

\bibitem{K07}
K.~Sakai, \emph{Nontrivalent graph cocycle and cohomology of the long knot space},
 Algebr.\ Geom.\ Topol.\ \textbf{8} (2008), 1499--1522.

\bibitem{KWatanabe08}
K.~Sakai and T.~Watanabe, \emph{1-loop graphs and configuration space integral for embedding spaces},
 in preparation, draft available at
http://www.ms.u-tokyo.ac.jp/\~{}ksakai/index.html

\bibitem{Sinha04}
D.~Sinha, \emph{ Operads and knot spaces},
 J.\ Amer.\ Math.\ Soc., \textbf{19}, no.\ 2 (2006), 461--486.

\bibitem{Tourtchine04_2}
V.~{Tourtchine (Turchin)}, \emph{On the other side of the bialgebra of chord diagrams},
 J.\ Knot Theory Ramifications \textbf{16} (2007), no.~5, 575--629.

\bibitem{Vassiliev01}
V.~Vassiliev, \emph{Combinatorial formulas for cohomology of knot spaces},
  Mosc.\ Math.\ J.\ \textbf{1} (2001), no.\ 1, 91--123.


\bibitem{Watanabe07}
T.~Watanabe, \emph{Configuration space integral for long $n$-knots and the Alexander polynomial},
 Algebr.\ Geom.\ Topol.\ \textbf{7} (2007), 47--92.
\end{thebibliography}
\end{document}