
\begin{thebibliography}{xxxxxx 89} 

\bibitem{kn:BC} Barlow, M.; \v Cern\'y, J.~(2011)\\
Convergence to fractional kinetics for random walks\\ associated with unbounded conductances,\\ 
{\em Probab.~Theory Related Fields}~{\bf 149}, 639--673.

\bibitem{kn:BBM} Ben Arous, G.; Bogatchev, L.; Molchanov, S.~(2005)\\ 
Limit Theorems for Sums of Random Exponentials,\\ 
{\em Probab.~Theory Related Fields}~{\bf 132}, no.~4, 579--612. 

\bibitem{kn:BBC} Ben Arous, G.; Bovier, A.; \v Cern\'y, J.~(2008)\\		
Universality of the REM for Dynamics of Mean-Field Spin Glasses,\\ 
{\em Comm.~Math.~Phys.}~{\bf 282}, no.~3, 663-695

\bibitem{kn:ABG1} Ben Arous, G.; Bovier, A.; Gayrard, V.~(2003)\\
Glauber dynamics of the random energy model.\\ I. Metastable motion on the extreme states,\\
{\em Comm.~Math.~Phys.}~{\bf 235}, no.~3, 379--425

\bibitem{kn:ABG2} Ben Arous, G.; Bovier, A.; Gayrard, V.~(2003)\\
Glauber dynamics of the random energy model.\\ II. Aging below the critical temperature,\\
{\em Comm.~Math.~Phys.}~{\bf 236}, no.~1, 1--54. 

\bibitem{kn:AC} Ben Arous, G.; \v Cern\'y, J.~(2005)\\
Bouchaud's model exhibits two different aging regimes in dimension one,\\
{\em Ann.~Appl.~Probab.}~{\bf 15}, no.~2, 1161--1192.

\bibitem{kn:AC1} Ben Arous, G.; \v Cern\'y, J.~(2007)\\
Scaling limit for trap models on $\Z^d$,\\
{\em Ann.~Probab.}~{\bf 35}, no.~6, 2356--2384. 

\bibitem{kn:AC2} Ben Arous, G.; \v Cern\'y, J.~(2008)\\
The arcsine law as a universal aging scheme for trap models,\\
{\em  Comm.~Pure Appl.~Math.}~{\bf 61}, no.~3, 289--329. 

\bibitem{kn:ACM} Ben Arous, G.; \v Cern\'y, J.; Mountford, T.~(2006)\\
Aging in two-dimensional Bouchaud's model,\\
{\em Probab.~Theory Related Fields}~{\bf 134}, 1--43.

\bibitem{kn:AFGH} Ben Arous, G.; Fribergh, A.; Gantert, N.; Hammond, H. (2012)\\
Biased random walks on a Galton-Watson tree with leaves,\\ 
{\em Ann.~Probab.}~{\bf 40}, 280--338 

\bibitem{kn:B} Bertoin, J.~(1999)\\
Subordinators: examples and applications\\
{\em Lecture Notes in Math.}~{\bf 1717}, 1-91, Springer

\bibitem{kn:Bou} Bouchaud, J.-P.~(1992)\\
Weak ergodicity breaking and aging in disordered systems,\\
{\em J.~Phys.~I France} {\bf 2}, 1705--1713.

\bibitem{kn:BD} Bouchaud, J.-P.; Dean, D.~S.~(1995)\\
Aging on Parisi's tree,\\
{\em J.~Phys.~I France} {\bf 5}, 265--286.

\bibitem{kn:BCKM} Bouchaud, J.-P.; Cugliandolo, L.; Kurchan, J.; M\'{e}zard, M.~(1998)\\
Out of equilibrium dynamics in spin-glasses and other glassy systems,\\
in {\em Spin-glasses and Random Fields} (A.P.~Young, Ed.), World Scientific

\bibitem{kn:BF} Bovier, A.; Faggionato, A.~(2005)\\
Spectral characterisation of ageing:\\ 
the REM-like trap model in the complete graph,\\
{\em Ann.~Appl.~Probab.}~{\bf 15}, 1997--2037 

\bibitem{kn:C} \v Cern\'y, J.~(2003)\\
Ph.D.~Thesis, Ecole Polytechnique F\' ed\' erale de Lausanne

\bibitem{kn:C2} \v Cern\'y, J.~(2011)\\
On two-dimensional random walk among heavy-tailed conductances,\\
Electronic Journal of Probability~{\bf 16}, 293--313

\bibitem{kn:FIN} Fontes, L.R.G.; Isopi, M.; Newman, C.~M.~(2002)\\
Random walks with strongly inhomogeneous rates and singular diffusions:\\ 
convergence, localization and aging in one dimension,\\
{\em Ann.~Probab.}~{\bf 30}, 579-604

\bibitem{kn:FL} Fontes, L.R.G.; Lima, P.H.S.~(2009)\\
Convergence of Symmetric Trap Models in the Hypercube.\\
In: XVth International Congress on Mathematical Physics, 2006, Rio de Janeiro.\\
{\em New Trends in Mathematical Physics}, Springer, 285-297.

\bibitem{kn:FM} Fontes, L.R.G. ; Mathieu, P.~(2008)\\
K-processes, scaling limit and aging for the trap model in the complete graph,\\
{\em Ann.~Probab.}~{\bf 36}, 1322-1358. 

\bibitem{kn:JP1} Jain, N.C.; Pruitt, W.E.~(1970)\\
The range of recurrent random walk in the plane, \\
{\em Z.~Wahrscheinlichkeitstheorie und Verw.~Gebiete}~{\bf 16}, 279--292.

\bibitem{kn:JP2} Jain, N.C.; Pruitt, W.E.~(1972)\\
The range of random walk,\\ 
{\em Proceedings of the Sixth Berkeley Symposium on Mathematical Statistics\\ 
and Probability~{\bf III}: Probability theory}, 31--50. 
Univ.~California Press.

%\bibitem{kn:KS} Kesten, H.; Spitzer, F.~(1963)\\
%Ratio theorems for random walks.~I. \\
%{\em J.~Analyse Math.}~{\bf  11}, 285--322. 

\bibitem{kn:L} Le Gall, J.-F.~(1986)\\
Propriet\'es  d'intersection des marches al\'eatoires.\\ I.~Convergence vers le temps local d'intersection.\\
{\em Comm.~Math.~Phys.}~{\bf 104}, no.~3, 471--507.

\bibitem{kn:LR} Le Gall, J.-F.; Rosen, J.~(1991)\\
The range of stable random walks, \\
{\em Ann.~Probab.}~{\bf 19}, no.~2, 650--705

\bibitem{kn:M} Mourrat, J.-C.~(2011)\\
Scaling limit of the random walk among random traps on $\Z^d$\\
{\em Ann.~Inst.~H.~Poincaré Probab.~Statist.}~{\bf 47}, no.~3, 813--849 


\bibitem{kn:Se} Seneta, E.~(1976)\\ Regularly varying functions.\\ {\em Lecture Notes in Mathematics}~{\bf 508}, Springer

\bibitem{kn:S} Spitzer, F.~(1976)\\ {\em Principles of random walks.} Second edition. Springer

%\bibitem{kn:EK} Ethier, S.N.; Kurtz, T.G.~(1986)\\
%{\em Markov processes. Characterization and convergence}, Wiley

%\bibitem{kn:S} Sharpe, M.~(1988)\\
%{\em General theory of Markov processes}, Academic Press

%\bibitem{kn:F} Feller, W.~(1971)\\
%{\em An introduction to probability theory and its applications,}
%Vol.~II, 2nd ed., Wiley

\end{thebibliography}
