\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}


\newtheorem{theorem}{Theorem}
\newtheorem{problem}{Problem}
\newtheorem{question}{Question}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}

\newtheorem{remark}[theorem]{Remark}
\newcommand{\M}{\mathcal{M}}
\newcommand{\one}{\mathbf{1}}
\title{Exponential Lower Bounds on Spectrahedral Representations of Hyperbolicity Cones \thanks{This research was supported by NSF Grants CCF-1553751,
 NSF CCF-1343104 and NSF CCF-1407779, and a Sloan Research Fellowship for NS.}}
\author{Prasad Raghavendra\\ EECS\\ UC Berkeley \and Nick Ryder\\Mathematics\\UC Berkeley \and Nikhil Srivastava\\Mathematics\\UC Berkeley \and Benjamin Weitz\\Pinterest}
\begin{document}
\maketitle
\begin{abstract}
The Generalized Lax Conjecture asks whether every hyperbolicity cone is a
	section of a semidefinite cone of sufficiently high dimension. We prove
	that the space of hyperbolicity cones of hyperbolic polynomials of
	degree $d$ in $n$ variables contains $(n/d)^{\Omega(d)}$ pairwise
	distant cones in the Hausdorff metric, and therefore that any semidefinite
	representation of such polynomials must have dimension at least
	$(n/d)^{\Omega(d)}$ (even allowing a small approximation error). The cones are perturbations of the hyperbolicity cones of
	elementary symmetric polynomials. Our proof contains several ingredients of
	independent interest, including the identification of a large subspace
	in which the elementary symmetric polynomials lie in the relative
	interior of the set of hyperbolic polynomials, and a quantitative
	generalization of the fact that a real-rooted polynomial with two
	consecutive zero coefficients must have a high multiplicity root at
	zero.
\end{abstract}
\input{intro}
%\input{prelims}
\input{manycones}
\input{restrictfar}
\input{conesfar}
\input{matrixfar}
\input{conclusion}
%\input{main.bbl}
%\bibliographystyle{amsalpha}
%\bibliography{hyperbolic}
\input{main.bbl}
\appendix
\section*{Appendix}
\begin{proof}[Proof of Lemma \ref{lem:jacobi}]
Let $z_1\le,\ldots,\le z_d=\lambda$ be the roots of $J(t)$. Observe that
$$J'(\lambda) = \prod_{i<d}(z_d-z_i)\ge |z_d-z_{d-1}|^{d-1},$$
so if we can prove a lowerbound on the spacing between $z_d$ and $z_{d-1}$ we are done.

We do this by recalling from Lemma \ref{eqn:jacobi} that:
$$J(t)=\frac{1}{d!}D^{n-d}t^{n-d}(1+t)^{d}.$$
Let $q_k(t):=D^{k}t^{n-d}(1+t)^{d}$ and note that $q_{k+1}$ interlaces $q_k$, and all of these polynomials have real roots in $[-1,0]$. Let $y_k$ be the largest root of $q_k$ that is strictly less than $0$, noting that every $q_k$ for $k<{n-d}$ has a root at $0$ because $q_0$ has a root of multiplicity $n-d$ at $0$. By lemma \ref{lem:aspect}, we have for $k=1,\ldots,n-d$:
$$y_{k+1}\le 0-\frac{1}{n}|0-y_{k}|\le -|y_k|/n.$$
Noting that $y_0=-1$ and iterating this bound $n-d-1$ times we obtain
$$y_{n-d-1}\le -1/n^{n-d-1},$$
so that $D^{n-d-1}q_0$ has a root at zero and a root $y_{n-d-1}\le -1/n^{n-d}.$ Since $J(t)=Dq_{n-d-1}(t)$, we must have $z_{d-1}\le -y_{n-d-1}$ by interlacing. However, applying Lemma \ref{lem:aspect} once more, we see that
$$ z_d\ge -y_{n-d-1}+|0+y_{n-d-1}|/n = -(1-1/n)y_{n-d-1},$$
so the gap must be at least
$$z_d-z_{d-1}\ge y_{n-d-1}/n = \frac{1}{n^{n-d}}.$$
Thus, we conclude that
$$J'(\lambda)\ge \frac{1}{n^{(d-1)(n-d)}}\ge \frac{1}{n^{d(n-d)}},$$
as desired.
\end{proof}

%,bib/tensor-pca}


\end{document}n
