I am deeply grateful to  Prof.\ Marc Lackenby for having been an exceptional supervisor. I greatly appreciate how, back when I had just begun my DPhil, he took care of orienting me across the research environment at Oxford, and made sure that my background was solid enough before I started any research. During these years he has promptly aided me when I have been in need for new ideas, or hints, to carry on my work; and assisted me in the key steps of my course. On the other hand, his balanced supervision has been crucial for me to start learning how to carry out independent research.

I wish to thank all the people with whom I have had profitable conversations for my work and understanding of the topic, including my {\it viva} examiners: Saul Schleimer and Panos Papazoglou; people I met at academic events: Bert Wiest, Jeffrey Brock, Ian Agol, Javier Aramayona; my examiners in occasion of my Transfer and Confirmation of Status: Martin Bridson and Cornelia Drutu; and anyone who have contributed to broadening my horizons. Thanks to Prof.\ Minhyong Kim for being my advisor at Merton College. Also, I am very indebted to Prof.\ Bruno Martelli, for giving me the opportunity to speak in my old university, and to Prof.\ Roberto Frigerio, who has been my supervisor at the time of my Bachelor and left me enthusiastic about low-dimensional topology.

It has been an honor for me to collaborate with Professors Alexander Ritter, Ulrike Tillman, and the already mentioned Papazoglou, Lackenby, and Drutu in undergraduate teaching. My teaching experience at Exeter College with the latter has been particularly rewarding and educational for me, and I am looking forward to starting my job as a Lecturer there in few weeks.

I am grateful to Merton College and to the Mathematical Institute for having been two enviable environments where to work and spend my everyday life in Oxford: thanks to their staff, for their professionalism, their time and effort. Moreover, I wish to acknowledge the irreplaceable financial support of the Scatcherd European Fund, along with the aforementioned institutions.